Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-05-06 doc/network.tex
working on methods

First, we begin by randomly selecting initially infected individuals; these individuals are assumed to be infected at $t = 0$.
For each infected individual $i$, we randomly draw a random number $E_i$ from an Erlang distribution with mean $1/\sigma$ and shape $n_E$ to represent the length of their latent period.
Given a total contact rate of $S_i \lambda$, where $S_i$ is the number of susceptible acquaintances and $\lambda$ is the per-pair contact rate, and a transition rate of $n_I \gamma$ between each infectious stages, 
the total number of contacts that an indiviudal $i$ in infectious stage $j$ makes before moving to infectious stage $j+1$ follows a geometric distribution with probability $n_I\gamma/(S_i \lambda + n_I\gamma)$:
\begin{equation}
C_{i, j} \sim \mathrm{Geometric}\left(\frac{n_I\gamma}{S_i \lambda + n_I\gamma}\right).
\end{equation}
For each contact, a contactee is uniformly sampled from the set of acquaintances of the individual $i$.
Then, the time between two events follows an exponential distribution with rate $S_i \lambda + n_I\gamma$:
\begin{equation}
T_{i, j, k} \sim \mathrm{Exponential}\left(S_i \lambda + n_I\gamma\right),
\end{equation}
where $k = 1, 2, \dots, C_{i, j}, C_{i, j} + 1$. Here, the $(C_{i, j} + 1)$-th event is the transition from the infectious stage from $j$ to $j+1$.
This process is repeated until the individual fully recovers (i.e., goes through all infectious stages).
Then, the time at which individual $i$ makes $k$-th contact is given by the sum of current time $t$, the length of latent period $E_i$, and the time between all events (either a contact or transistion between states) caused by this individual prior to the contact:
\begin{equation}
\begin{cases}
t + E_i + \sum_{n=1}^k T_{i, j, n}, & \text{if } j = 1,\\
t + E_i + \sum_{m=1}^{j-1} \sum_{n=1}^{C_{i, m} + 1} T_{i, m, n} + \sum_{n=1}^k T_{i, j, n}, & \text{if } j > 1,
\end{cases}
\end{equation}

>>>>

First, we begin by randomly selecting initially infected individuals; these individuals are assumed to be infected at $t = 0$.
For each infected individual $i$, we randomly draw a random number $E_i$ from an Erlang distribution with mean $1/\sigma$ and shape $n_E$ to represent the length of their latent period.
Given a total contact rate of $S_i \lambda$, where $S_i$ is the number of susceptible acquaintances and $\lambda$ is the per-pair contact rate, and a transition rate of $n_I \gamma$ between each infectious stages, 
the total number of contacts that an indiviudal $i$ in infectious stage $j$ makes before moving to infectious stage $j+1$ follows a geometric distribution with probability $n_I\gamma/(S_i \lambda + n_I\gamma)$:
\begin{equation}
C_{i, j} \sim \mathrm{Geometric}\left(\frac{n_I\gamma}{S_i \lambda + n_I\gamma}\right).
\end{equation}
For each contact, a contactee is uniformly sampled from the set of acquaintances of the individual $i$.
Then, the time between two events follows an exponential distribution with rate $S_i \lambda + n_I\gamma$:
\begin{equation}
T_{i, j, k} \sim \mathrm{Exponential}\left(S_i \lambda + n_I\gamma\right),
\end{equation}
where $k = 1, 2, \dots, C_{i, j}, C_{i, j} + 1$. Here, the $(C_{i, j} + 1)$-th event is the transition from the infectious stage from $j$ to $j+1$.
This process is repeated until the individual fully recovers (i.e., goes through all infectious stages).
Then, the (yet to be realized) generation time between individual $i$ and the $k$-th contactee (during infectious stage $j$) is equal the sum of the length of latent period $E_i$ and the time between all events (either a contact or transistion between states) caused by this individual prior to the contact:
\begin{equation}
G_{i,j,k} = \begin{cases}
E_i + \sum_{n=1}^k T_{i, j, n}, & \text{if } j = 1,\\
E_i + \sum_{m=1}^{j-1} \sum_{n=1}^{C_{i, m} + 1} T_{i, m, n} + \sum_{n=1}^k T_{i, j, n}, & \text{if } j > 1.
\end{cases}
\end{equation}
Finally, the time at which this individual is contacted by individual $i$ is equal to the sum of current time $t$ and the generation time $G_{i,j,k}$.

After repeating the contact process for all initially infected individuals, all contacts are put into a sorted queue.
The first person in the queue becomes infected, and the current time is updated to infection time of this individual. 
Any subsequent contacts made to this individual are removed from the queue because they will no longer be effective.
We repeat the contact process for this newly infected individual.
Then, new contacts are added to the sorted queue.
Simulation continues until there are no more contacts are left in the queue.
